### 2024-05-19 index.qmd
20240514 - error, message, warning
20240514 - remove code chunk that was throwing an error
20240516 - section headings for cross-reference
20240519 - acknowledgments
20240519 - FFA

# Preface {.unnumbered .unlisted}

@@

The following code chunk throws an error if I remove it:

```{r}
1 + 1
```

@@

>>>>

# Preface {#sec-preface .unnumbered .unlisted}

@@

@@

I thank Benjamin Motz, who provided consultation and many helpful resources based on his fantasy football statistics class.
I also thank key members of [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), including Val Pinskiy, Andrew Tungate, Dennis Andersen, and Adam Peterson, who helped develop and provide fantasy football-related resources and who helped sharpen my thinking about the topic.
